STA610 Case Study 1 Team 4 Report

### 2021-03-21 STA 610 Case Study 1 Report_Team 4.Rmd
Code added for finding influential observations based on Cook's distance

```{r}
mod1b.inf <- influence(mod1b, maxfun=1)
infIndexPlot(mod1b.inf, vars='Cook')
```

```{r}
#mod1 <- lmer(data=df, log_ppm ~ (1 | state) + date_num + mgstr + bulk_purchase + Primary_Reason + source)
#mod1b <- lmer(data=df, log_ppm ~ (1 | state) + year + mgstr + bulk_purchase + Primary_Reason + source)
big_data <- df[!influential,]
mod1c <- lmer(data=big_data, log_ppm ~ (1 | state) + year + mgstr + bulk_purchase + Primary_Reason + source)
qqmath(mod1c)
```

>>>>

```{r}
mod1b.inf <- influence(mod1b, maxfun=1)

infIndexPlot(mod1b.inf, vars='Cook')

# Find the most influential observations
high_inf_idx <- order(cooks.distance(mod1b.inf), decreasing = TRUE)

# Take a look at some of the most influential observations
df[high_inf_idx[1:25], ]
```

```{r}
#mod1 <- lmer(data=df, log_ppm ~ (1 | state) + date_num + mgstr + bulk_purchase + Primary_Reason + source)
#mod1b <- lmer(data=df, log_ppm ~ (1 | state) + year + mgstr + bulk_purchase + Primary_Reason + source)
better_data <- df %>% filter(ppm > 0.2)
mod1c <- lmer(data=better_data, log_ppm ~ (1 | state) + date_num + year + mgstr + bulk_purchase + Primary_Reason + source)
qqmath(mod1c)
```
